\section*{J5 - Strictly Increasing}
Mr. Lane is learning about sequences. In particular, he is learning about strictly increasing sequences—sequences in which each term is strictly greater than the last; that is, $a_N>a_{N−1}$.

For example, the sequence $1,2,4,5,9$ is strictly increasing, whereas $2,5,5,6$ is not.

One particular question in his homework asks him to determine the corresponding strictly increasing sequence given $N$, the number of terms in the sequence, as well as $a_1$ and $a_N$, the first and last terms of the sequence, respectively.

Knowing that there can be multiple sequences that meet this criteria, the teacher provides the class with a list of strictly increasing sequences they are to choose from. Unfortunately, Mr. Lane has lost his sheet and has chosen to guess the correct answer rather than asking for a new sheet. Before he guesses, he wants to know the chance of him guessing the correct solution.

Help Mr. Lane determine the number of possible sequences of length $N$ and whose first and last elements are $a_1$ and $a_N$ respectively.

\inputformat
The first line of input consists of a single integer $N$ describing the number of terms in the strictly increasing sequence. The second line of input consists of two space-separated integers $a_1$ and $a_N$ representing the first and last terms of the sequence respectively.

\constraints
For all subtasks, $1 \leq a_1, a_N \leq 10^6$ and $N \geq 3$.

\textbf{Subtask 1 [10\%]} \\
$N \leq 10$ 

\textbf{Subtask 2 [90\%]} \\
$N \leq 10^4$

\outputformat
Output the number of possible sequences. If no such sequence exists, output $0$.

\addsample
{
    4 \\
    1 5
}
{
    3
}