\section*{S4 - The Cost of War}
In any war, an important consideration for an army is \textit{funding}. After all, wars can be expensive and an army is only as strong as its finances allows them to be. However, funding is secondary to strategy. After all, a well-funded army with no strategy will surely be beaten by a poor army with astounding strategy.

One particular army, the army of Kalisha, has $N$ bases that they want to connect in order to ensure fast and easy transportation of food, troops, and equipment. However, after reaching out to a contractor, they determine that connecting roads \textit{extremely} expensive to build.

With strategy having priority over cost, the army of Kalisha needs to ensure all bases are connected - either directly or indirectly. However, in doing so, they also need to ensure that they are minimizing the cost of building the connecting roads. 

Help them determine the minimum cost of connecting their bases!

\inputformat
The first line of input contains two space-separated integers $N$ and $M$, the number of bases, and the number of possible roads. The next $M$ lines of input contains three space-separated integers $a$, $b$, and $c$, indicating that bases $a$ and $b$ can be connected at cost $c$.

\constraints
$2 \leq N \leq 1\;000$ \\
$1 \leq M \leq 5\;000$ \\
$1 \leq a, b \leq N$ \\
$1 \leq c \leq 1\;000$

\outputformat
The output consists of a single integer, the minimum cost to connect all the bases.

\addsample
{
    4 5 \\
    1 2 10 \\
    2 3 12 \\
    3 4 3 \\
    4 1 9 \\
    1 3 30
}
{
    22
}